---
title: "Inferential Statistics - Course Project 6"
author: "Maurizio Murino"
date: "25 January 2016"
output: html_document
---

## Introduction

_In this project you will investigate the exponential distribution in R and compare it with the Central Limit Theorem. The exponential distribution can be simulated in R with rexp(n, lambda) where lambda is the rate parameter. The mean of exponential distribution is 1/lambda and the standard deviation is also 1/lambda. Set lambda = 0.2 for all of the simulations. You will investigate the distribution of averages of 40 exponentials. Note that you will need to do a thousand simulations._

Illustrate via simulation and associated explanatory text the properties of the distribution of the mean of 40 exponentials. 

## Simulations
_Include English explanations of the simulations you ran, with the accompanying R code._

Set `lambda` to 0.2.

```{r}
lambda <- 0.2
```

I create a first data object `dt1` with a vectorized operation. When possible, I prefer this approach rather than a loop function. I set `set.seed(123)`. 

```{r}
set.seed(123)
dt1 <- replicate(1000, mean(rexp(40, lambda)))
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.

## Sample Mean versus Theoretical Mean 
_Include figures with titles. In the figures, highlight the means you are comparing. Include text that explains the figures and what is shown on them, and provides appropriate numbers._

The sample mean is not very distant from the theoretical mean.

```{r}
s_mean <- mean(dt1)
th_mean <- 1/lambda
s_mean
th_mean
```

Now I am going to graphically compare the distribution of data `dt1` abouth the means.

```{r show hist and means}
hist(dt1)
```

Sample Variance versus Theoretical Variance: Include figures (output from R) with titles. Highlight the variances you are comparing. Include text that explains your understanding of the differences of the variances.
Distribution: Via figures and text, explain how one can tell the distribution is approximately normal.
